---
title: "Package Integration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package Integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The **logr** package can be used as a logging system for R packages.  The
system is best suited for cases where you need a complete, SAS®-like log.
It has functions to generate errors, warnings, and informative messages. The 
log header and footer are produced automatically. Notes
and timestamps are already built in. In short, the **logr** package takes 
care of all the tedious details of logging, and lets you concentrate on documenting
key activities and providing valuable feedback to your user. 

There are two types of logging you may want to offer with your custom R package: 
direct logging, and indirect logging.  

Direct logging means you want your
package to create its own log.  Indirect logging means the user of your package
will be creating a log, and you want your package to contribute to the user's
log.  Below are some considerations for each of these two types of logging.

### Direct Logging

To integrate the **logr** package into your custom R package, take the following
steps for direct logging:

1) Add **logr** to the "imports" section of your DESCRIPTION file.
2) Add the directive "@import logr" to at least one roxygen function header.
3) Add **logr** calls to your functions as desired.

For this type of logging, there is normally a "main" or driver function, 
which branches to several subroutines.  In this case, place the `log_open()`
and `log_close()` function calls in the "main" function.  Then place 
`log_print()` or `put()` calls in the subroutines.  The printing functions 
will output to the log as expected.  

For direct logging, you may also use the `log_error()`, `log_warning()`, 
and `log_info()` functions as needed.  Note that `log_error()` will not stop execution
of your function calls.  It will simply log the appropriate message and keep going.
To stop execution of your function, use the Base R `stop()` function.

Also note that `log_error()`, `log_warning()` and `log_info()` will send messages
to the console.  This feature is useful for notifying the user of what is going
on with your package.

### Indirect Logging

For indirect logging, the user will be creating their own log, and you want
your package to write messages to their log.  

For example, you may be creating
a package of utility functions, and the user is using your utility functions to 
write a program.  The program will have the calls to `log_open()` and `log_close()`,
but you want your utility functions to send messages to the program log.  This outcome
can be achieved with the logging hook.

#### Logging Hook

The **logr** package provides a special function, `log_hook()`, specifically
designed for logging common informational messages from a custom package.  The
function is intended to be used in cases where you want to send items to the log, 
but not send anything to the console. In other words, the `log_hook()` function
is for when you want to log things quietly and invisibly.  

To use indirect logging, take the following steps:

1) Add **logr** to the "suggests" section of your DESCRIPTION file.
2) Do not add the directive "@import logr" to any roxygen function header.
3) Do check to ensure **logr** is installed on the local machine.
4) Add `logr::log_hook()` calls to your functions as desired, using the double
colon full package reference.

When called, the `log_hook()` function will first check to see whether the user's 
log is open.  If open, the function will then write the message to the user's log.
If a log is not open, the message will be ignored.  This feature is useful to 
avoid "log not open" warnings from the **logr** package.

Additionally, the `log_hook()` function is integrated with the "autolog" feature.
In other words, `log_hook()` will only work when "autolog" is turned on.  That
means the user will be able to turn off your custom logging messages by turning
off "autolog". This feature gives the user some control over whether routine messages
from your package are logged or not.

The example below shows a custom function, where the function output is 
logged automatically using `log_hook()`:

```{r eval=FALSE, echo=TRUE}
#' @title Read an RDS file
#' @param file_path The path to the file. 
#' @return The RDS file contents as an R object.
#' @export
read_file <- function(file_path) {
  
  ret <-  readRDS(file_path)
  
  if (length(find.package('logr', quiet=TRUE)) > 0) {
    logr::log_hook(paste0("Read RDS file from '", file_path, "'"))
  }
  
  return(ret)
}
```
The above function simply reads in an RDS file and returns the contents to the 
user. What is different about this function is that it will record the operation
in the user's log automatically via `log_hook()`.  This integration allows you
to provide automatic, invisible logging to your users in the most seamless
way possible.

#### Indirect Logging of Errors and Warnings 

For indirect logging of errors and warnings, it is recommended to use 
the `stop()` and `warning()` Base R functions, instead of `log_error()` and
`log_warning()`.  The logger package will trap these Base R functions, and send
the message to the log. The `stop()` command will also stop execution of your
function. Stopping execution of the function is normally what is intended
when an error occurs.


Next: [Complete Example](logr-example1.html)


