---
title: "Aliases for log_print()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Aliases for log_print()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Note that the `log_print()` function has two aliases: `put()` and `sep()`.  

The `put()` function is exactly like `log_print()`, but it is shorter
and easier to type. 

The `sep()` function is a slight variant of `log_print()`
that prints separators above and below the message text.  It is useful for 
creating sections in your log.  Breaking your log into sections makes it easier
to read and understand.

Here is example showing these aliases at work:

```{r eval=FALSE, echo=TRUE}
library(logr)
library(magrittr)

# Create temp file location
tmp <- file.path(tempdir(), "test.log")

# Open log
lf <- log_open(tmp)

# Create log section
sep("Illustration of put() and sep()")

# Send message to log
put("High Mileage Cars Subset")

# Perform operations
hmc <- subset(mtcars, mtcars$mpg > 20) %>% 
  put() # prints pipeline result to log

# Close log
log_close()

# View results
writeLines(readLines(lf))

```

Here is the log from the above alias example:

```
========================================================================= 
Log Path: C:/Users/User/AppData/Local/Temp/RtmpioAPbg/log/test.log 
Working Directory: C:/packages/Testing 
User Name: User 
R Version: 4.0.3 (2020-10-10) 
Machine: DESKTOP-1F27OR8 x86-64 
Operating System: Windows 10 x64 build 18363 
Log Start Time: 2020-12-21 14:18:33 
========================================================================= 

========================================================================= 
Illustration of put() and sep() 
========================================================================= 

High Mileage Cars Subset 

                mpg cyl  disp  hp drat    wt  qsec vs am gear carb
Mazda RX4      21.0   6 160.0 110 3.90 2.620 16.46  0  1    4    4
Mazda RX4 Wag  21.0   6 160.0 110 3.90 2.875 17.02  0  1    4    4
Datsun 710     22.8   4 108.0  93 3.85 2.320 18.61  1  1    4    1
Hornet 4 Drive 21.4   6 258.0 110 3.08 3.215 19.44  1  0    3    1
Merc 240D      24.4   4 146.7  62 3.69 3.190 20.00  1  0    4    2
Merc 230       22.8   4 140.8  95 3.92 3.150 22.90  1  0    4    2
Fiat 128       32.4   4  78.7  66 4.08 2.200 19.47  1  1    4    1
Honda Civic    30.4   4  75.7  52 4.93 1.615 18.52  1  1    4    2
Toyota Corolla 33.9   4  71.1  65 4.22 1.835 19.90  1  1    4    1
Toyota Corona  21.5   4 120.1  97 3.70 2.465 20.01  1  0    3    1
Fiat X1-9      27.3   4  79.0  66 4.08 1.935 18.90  1  1    4    1
Porsche 914-2  26.0   4 120.3  91 4.43 2.140 16.70  0  1    5    2
Lotus Europa   30.4   4  95.1 113 3.77 1.513 16.90  1  1    5    2
Volvo 142E     21.4   4 121.0 109 4.11 2.780 18.60  1  1    4    2

========================================================================= 
Log End Time: 2020-12-21 14:18:33 
Log Elapsed Time: 0 00:00:00 
========================================================================= 
```

Next: [tidylog Integration](https://logr.r-sassy.org/articles/logr-tidylog.html)